Poster Data Analysis

### 2018-09-08 notebooks/poster_analysis.Rmd
updated heatmap to include NA values

megares_long <- megares_results %>%
  gather(gene, value, -c(id, type)) %>%
  filter(is.na(value) == FALSE)

@@

megares_long %>%
  rbind(resfinder_long) %>%
  mutate(type2 = ifelse(type == "mut", 1, 2)) %>%
  spread(id, value, fill = 0) %>%
  gather(key = "id", value = "result", -c(gene, type, type2)) %>%
  left_join(species_data, by = "id") %>%
  ggplot(aes(fct_reorder(gene, type2),
             factor(id,
                    levels = unique(.[order(.$species,
                                                          .$id),
                                                    "id",
                                                    drop = TRUE])),
             fill = species,
             alpha = result)) +
  geom_tile(color = "white")+
  geom_vline(xintercept = 14.5)+
  scale_fill_brewer(palette = "Paired")+
  theme_minimal()+
  labs(fill = NULL)+
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1,
                                   vjust = 0.3,
                                   size = 7),
        axis.title = element_blank(),
        axis.text.y = element_blank(),
        panel.grid = element_blank(),
        legend.position = "right")+
  guides(alpha = FALSE)+
  coord_fixed()
```

>>>>

megares_long <- megares_results %>%
  gather(gene, value, -c(id, type))

@@

megares_long %>%
  rbind(resfinder_long) %>%
  mutate(type2 = ifelse(type == "mut", 1, 2),
         value = factor(ifelse(is.na(value) == TRUE, 2, value))) %>%
  spread(id, value, fill = 0) %>%
  gather(key = "id", value = "result", -c(gene, type, type2)) %>%
  left_join(species_data, by = "id") %>%
  mutate(result = ifelse(result == 2, NA, result),
         fillcol = paste(species, result, sep = "_"),
         fillcol = ifelse(is.na(result) == TRUE, NA, fillcol)) %>%
  ggplot(aes(fct_reorder(gene, type2),
             factor(id,
                    levels = unique(.[order(.$species,.$id),"id",drop = TRUE])),
             fill = fillcol,
             alpha = result)) +
  geom_tile(color = "white")+
  geom_vline(xintercept = 14.5)+
  scale_fill_brewer(palette = "Paired",
                    na.value = "#6b6767")+
  theme_minimal()+
  labs(fill = NULL)+
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1,
                                   vjust = 0.3,
                                   size = 7),
        axis.title = element_blank(),
        axis.text.y = element_blank(),
        panel.grid = element_blank(),
        legend.position = "right")+
  guides(alpha = FALSE)+
  coord_fixed()

```
